---
output: 
  officedown::rdocx_document:
    reference_docx: "Formatvorlage_autoValWORD.docx"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: 'Figure '
       sep: ': '
---

```{r setup, echo=FALSE, message = FALSE}

library(knitr)
library(tidyverse)
library(parallel)
library(robslopes)
library(readxl)
library(officedown)
library(officer)
library(mcr)
library(flextable)
set_flextable_defaults(font.size = 11, padding = 3)
use_df_printer()
opts_chunk$set(echo = TRUE, ft.align = "center", fig.align = "center")
```

<!-- Prepare libraries and import data from Excel -->

<!-- create vectors method.x and method.y, run Passing Bablok regression -->

<!-- change column names in PB.reg@mnames to prepare for dynamic title-, axis- & legend labels-->

```{r Datentabelle, echo=FALSE, message = FALSE}
library(readxl)
## Import Data from a xlsx file, create the vectors for reference x and test y
validation.data <- read_excel("vdata.xlsx", sheet = "DATA")
val.crit <- read_excel("vdata.xlsx", sheet = "CRIT")
val.info <- read_excel("vdata.xlsx", sheet = "INFO")
val.prec <- read_excel("vdata.xlsx", sheet = "PREC")

method.x <- validation.data[[1]]
method.y <- validation.data[[2]]
## PaBa (formal class names: PB.reg) regression, rename column titles in PB.reg@mnames
PB.reg <- mcreg(method.x,method.y, method.reg = "PaBa")
PB.reg@mnames[1] <- colnames(validation.data)[1]
PB.reg@mnames[2] <- colnames(validation.data)[2]

```

---
title: "`r paste(val.info$x[1])`"  
---  
  
# Einleitung 


```{r cover_table, echo = FALSE, message = FALSE}

val.info |>  flextable() |> 
  bold(i = c(1, 11, 15, 17)) |> 
  theme_vanilla() |>   
  bg(bg = "darkgrey", i = 1) |> 
  bg(bg = "lightgrey", i = c(11, 15, 17)) |> 
  set_table_properties(width = 0.8, layout = "autofit") |> 
  colformat_date(fmt_date = "%d/%m/%Y")

```


\newpage
# ZUSAMMENFASSUNG DER MESSERGEBNISSE UND DATENAUSWERTUNG
## Messdaten, Mittelwerte und Differenzen 
  
```{r data_table, echo = FALSE, warning = FALSE, message = FALSE}
table.one <- data.frame(seq.int(nrow(validation.data)),validation.data)
colnames(table.one)[1] = "# "

table.one$"delta.%" <- (round((table.one[[3]]-table.one[[2]])
                        *100/mean(table.one[[2]]+table.one[[3]]), digits = 1))

table.one |> 
  flextable() |>  
  theme_vanilla() |>  
  bg(bg = "grey", part = "header") |> 
  align(align = "center", part = "all") |> 
  bg(j = 4, bg = scales::col_numeric(palette = c("red", "green", "yellow"), domain = c(-20, 20))) |> 
  set_table_properties(width = 0.5, layout = "autofit")
```

\newpage

## Präzisionsdaten

```{r intra_and_inter_assay_coefficient_of_variability, echo = FALSE, message = FALSE}
library(tidyverse)
library(flextable)

cv <- function(x) {
  sd(x) * 100 / mean(x)
}

prec.data <-
  val.prec |> select(Messwert_intra1,
                     Messwert_intra2,
                     Messwert_inter1,
                     Messwert_inter2)

prec.data.stat <-
  prec.data |> summarize(n = n(), across(
    Messwert_intra1:Messwert_inter2,
    list(
      Mittelwert = \(x) round(mean(x, na.rm = TRUE), digits = 2),
      StabW = \(x) round(sd(x, na.rm = TRUE), digits = 2),
      VK = \(x) round(cv(x), digits = 1)
    )
  ),)



intra.df <- data.frame(
  "Intra Assay" = c("n", "Zielwert", "Mittelwert", "SD", "VK (%)"),
  L = c(
    paste(prec.data.stat$n),
    paste(val.prec$Ziel_intra1[1]),
    paste(prec.data.stat$Messwert_intra1_Mittelwert),
    paste(prec.data.stat$Messwert_intra1_StabW),
    paste(prec.data.stat$Messwert_intra1_VK)
  ),
  H = c(
    paste(prec.data.stat$n),
    paste(val.prec$Ziel_intra2[1]),
    paste(prec.data.stat$Messwert_intra2_Mittelwert),
    paste(prec.data.stat$Messwert_intra2_StabW),
    paste(prec.data.stat$Messwert_intra2_VK)
  )
)

inter.df <- data.frame(
  "Inter Assay" = c("n", "Zielwert", "Mittelwert", "SD", "VK (%)"),
  L = c(
    paste(prec.data.stat$n),
    paste(val.prec$Ziel_inter1[1]),
    paste(prec.data.stat$Messwert_inter1_Mittelwert),
    paste(prec.data.stat$Messwert_inter1_StabW),
    paste(prec.data.stat$Messwert_inter1_VK)
  ),
  H = c(
    paste(prec.data.stat$n),
    paste(val.prec$Ziel_inter2[1]),
    paste(prec.data.stat$Messwert_inter2_Mittelwert),
    paste(prec.data.stat$Messwert_inter2_StabW),
    paste(prec.data.stat$Messwert_inter2_VK)
  )
)


```


```{r intra_assay_table, echo = FALSE, message = FALSE, warning = FALSE}
intra.df.ft <- flextable(intra.df)
intra.df.ft <- align(intra.df.ft, align = "right", part = "all")
intra.df.ft <- autofit(intra.df.ft)
intra.df.ft <- add_footer_lines(intra.df.ft, "")
intra.df.ft |> bg(bg = "grey", part = "header")

```
  

```{r inter_assay_table, echo = FALSE, message = FALSE, warning = FALSE}
inter.df.ft <- flextable(inter.df)
inter.df.ft <- align(inter.df.ft, align = "right", part = "all")
inter.df.ft <- autofit(inter.df.ft)
inter.df.ft |> bg(bg = "grey", part = "header")

```


## Korrelation

<!-- Pearsson correlation and plot, sample number n from PB.reg@data -->

```{r correlation, echo=FALSE, out.height = "80%", out.width = "80%"}

## Correlation plot with Pearsson correlation
## Creating the plot
plot(method.x, method.y, pch = 19, col = "#68228B", 
     xlab=colnames(validation.data)[1], ylab=colnames(validation.data)[2])

## Regression line
abline(lm(method.y ~ method.x), col = "red", lwd = 3)

## Pearson correlation
text(paste("Pearson's r:", round(cor(method.x, method.y), 2)), x=max(method.x)*0.85, y=max(method.y)*0.1)
text(paste("n=", nrow(PB.reg@data)), x=40, y=5)

```


\newpage
## Passing Bablok

<!-- Passing Bablok Plot mit Steigung, Achsenabschnitt, Spearman's correlation  -->

```{r PB, echo=FALSE, out.height = "80%", out.width = "80%"}

MCResult.plot(PB.reg, equal.axis = TRUE, x.lab = colnames(validation.data)[1], y.lab = colnames(validation.data)[2], points.col = "#68228B", points.pch = 19, ci.area = TRUE, ci.area.col = "#0000FF50", main = paste("Validation", colnames(validation.data)[2], "vs", colnames(validation.data)[1]), sub = "", add.cor = TRUE, cor.method = "spearman", add.grid = FALSE, points.cex = 1)
##Angabe Steigung und Achsenabschnitt und CI
intercept_est <- PB.reg@para[1]
intercept_lci <- PB.reg@para[5]
intercept_uci <- PB.reg@para[7]
gradient_est <- PB.reg@para[2]
gradient_lci <- PB.reg@para[6]
gradient_uci <- PB.reg@para[8]
alpha_ci <- PB.reg@alpha[1]
text(cex=.65,x=max(validation.data)*0.8,y=max(validation.data)*0.34,sprintf("Gradient : %4.2f (%4.2f - %4.2f)", gradient_est, gradient_lci, gradient_uci))
text(cex=.65,x=max(validation.data)*0.8,y=max(validation.data)*0.27,sprintf("Intercept : %4.2f (%4.2f - %4.2f)", intercept_est, intercept_lci, intercept_uci))
text(cex=.65,x=max(validation.data)*0.8,y=max(validation.data)*0.2, sprintf("alpha : %4.2f", alpha_ci))

```

```{r coef_plot, echo = FALSE, warning = FALSE, message = FALSE}
fitPaBa <- mcreg(as.matrix(validation.data), method.reg="PaBa", na.rm=TRUE)
fitlr <- mcreg(as.matrix(validation.data), method.reg="LinReg", na.rm=TRUE)
compareFit(fitlr, fitPaBa)
```

\newpage

## Bland-Altman

```{r BA, echo=FALSE, out.height = "80%", out.width = "80%"}
MCResult.plotDifference(PB.reg)
```

```{r BArel, echo=FALSE, out.height = "80%", out.width = "80%"}

MCResult.plotDifference(PB.reg, plot.type = 8, main = "rel Difference plot")
```

```{r Bias, echo=FALSE, out.height = "90%", out.width = "90%"}
## Calculation of models
m2 <- mcreg(method.x,method.y,method.reg="PaBa", method.ci="bootstrap",
            method.bootstrap.ci="BCa",mref.name=colnames(validation.data)[1],
            mtest.name=colnames(validation.data)[2], na.rm=TRUE)
## Drawing of proportional bias
plotBias(m2, ci.area=TRUE, ci.border=TRUE, cex.sub=0.2)

```

```{r Bias_prop, echo=FALSE, out.height = "90%", out.width = "90%"}
plotBias(m2, ci.area=TRUE, ci.border=TRUE, prop=TRUE, cex.sub=0.2)
```

\newpage

# Schlussfolgerung und Freigabe



<!-- User Input zur Beurteilung und Freigabe -->



```{r Schlussfolgerung, echo = FALSE}
block_pour_docx("blocks_Akzeptanzkriterien.docx")
```
---

**Zentrum für Labormedizin St. Gallen, `r paste(format(Sys.time(), '%A %d. %B %Y'))`**

\newpage

--- 

#### Data is processed using R language^1^, mcr package^2^ and flextable package^3^. Rmarkdown^4^, Officedown^5^ and Officer^6^ are used for converting results into Word, PDF and HTML files. This project was inspired by Daniel Holmes (UBC, CA)^7^, Burak Bahar (Washington, USA)^8^ and David Gohel (Roubaix, F)^9^.
  
#### References and packages:
  
1.  R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. Version: `r getRversion()` URL: <https://www.R-project.org>
2.  mcr: Method Comparison Regression. Version: `r packageDescription("mcr")$Version` URL: <http://CRAN.R-project.org/package=mcr>
3.  flextable: a framework for easily creating tables. Version: `r packageDescription("flextable")$Version` URL: <http://CRAN.R-project.org/package=flextable>
4.  rmarkdown: Dynamic Documents for R. Version: `r packageDescription("rmarkdown")$Version` URL: <http://rmarkdown.rstudio.com>
5.  officedown: Formatting Microsoft documents produced by RMarkdown. R Version: `r packageDescription("officedown")$Version` URL: <http://CRAN.R-project.org/package=officedown>
6.  officer: Manipulation of Microsoft Word and PowerPoint Documents. R Version: `r packageDescription("officer")$Version` URL: <http://CRAN.R-project.org/package=officer>
7.  The Lab-R-torian: URL: <https://labrtorian.com/>
8.  An interactive website for analytical method comparison and bias estimation: URL: <https://bahar.shinyapps.io/method_compare/>
9.  SOLUTIONS ET FORMATIONS EN DATA-SCIENCE: URL: <https://www.ardata.fr/>

---