---
output: 
  officedown::rdocx_document:
    reference_docx: "Formatvorlage_autoValWORD.docx"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: 'Figure '
       sep: ': '
params:
  method: "Default Method"       
---

```{r setup, echo=FALSE, message = FALSE, warning = FALSE}


 source("StartUp.R")
 StartUpRoutine()

set_flextable_defaults(font.size = 11, padding = 3)
use_df_printer()
opts_chunk$set(echo = TRUE, ft.align = "center", fig.align = "center")

method <- params$method

```



```{r Datentabelle, echo=FALSE, message = FALSE, warning = FALSE}

# Import Data from a the SQLite database

 query.dxi.val <- "SELECT DISTINCT
                        a.Werte AS DxI800,
                        d.DoseResult_c AS DxI9000,
                        a.Bezeichnung,
                        a.Methode,
                        m.EINHEIT AS Einheit_800,
                        d.DoseUnit AS Einheit_9000,
                        d.Probennummer
                      FROM MeasurementData a
                        JOIN MethodData m ON a.Methode = m.Methode
                        JOIN TranslationData t ON a.Methode = t.Methode
                        JOIN DxIvalData d ON t.TestOrderCode = d.TestOrderCode
                      WHERE a.Methode = '%s' AND a.Probennummer = d.Probennummer AND d.DoseResult <> 'No result';"
    
    # Fetch data from the database
    validation.data <- NULL
    validation.data <- dbGetQuery(con, sprintf(query.dxi.val, method))
    # convert data to numeric
    validation.data[,1] <- as.numeric(validation.data[,1])
    # validation.data[,2] <- as.numeric(validation.data[,2])
    
    # omit rows with NA values
    validation.data <- na.omit(validation.data)
    
```

```{r PBregprep, echo=FALSE, message=FALSE, warning=FALSE}
    
  
# this  needs further improvement, inadequate source!-------------------------------------
# val.crit <- read_excel("vdata _DxI.xlsx", sheet = "CRIT")
val.info <- read_excel("vdata _DxI.xlsx", sheet = "INFO")
names(val.info)[2:3] <- c(paste(unique(validation.data$Bezeichnung),
                                names(validation.data[1])),
                          paste(unique(validation.data$Bezeichnung),names(validation.data[2])))
val.prec <- read_excel("vdata _DxI.xlsx", sheet = "PREC")
##-------------------------------------------------------------------------------------
  
method.x <- as.numeric(validation.data[[1]])
method.y <- as.numeric(validation.data[[2]])

```

```{r PBreg, echo=FALSE, message=FALSE, warning=FALSE}

## PaBa (formal class names: PB.reg) regression, rename column titles in PB.reg@mnames
set.seed(8173)
#tryCatch({
  PB.reg <- mcreg(method.x,method.y, method.reg = "PaBa")
  PB.reg@mnames[1] <- colnames(validation.data)[1]
  PB.reg@mnames[2] <- colnames(validation.data)[2]
# }, error = function(e) {
#   print(e)
#   cat("Nicht genug Daten verfügbar für die Passing-Bablock-Regressionsanalyse")
#   stop()
# })


# PB.reg <- mcreg(method.x,method.y, method.reg = "PaBa")
# PB.reg@mnames[1] <- colnames(validation.data)[1]
# PB.reg@mnames[2] <- colnames(validation.data)[2]

```

---
title: "`r paste(val.info$x[1])`"  
---  
  
# Einleitung 


```{r cover_table, echo = FALSE, message = FALSE, warning = FALSE}

val.info |>  flextable() |> 
  bold(i = c(1, 11, 15, 17)) |> 
  theme_vanilla() |>   
  bg(bg = "darkgrey", i = 1) |> 
  bg(bg = "lightgrey", i = c(11, 15, 17)) |> 
  set_table_properties(width = 0.8, layout = "autofit") |> 
  colformat_date(fmt_date = "%d/%m/%Y")

```


\newpage
# ZUSAMMENFASSUNG DER MESSERGEBNISSE UND DATENAUSWERTUNG
## Messdaten, Mittelwerte und Differenzen 
  
```{r data_table, echo = FALSE, warning = FALSE, message = FALSE}
table.one <- data.frame(seq.int(nrow(validation.data)),validation.data[,c(1,5,2,6)])
colnames(table.one)[1]  <-  paste("# ",validation.data$Bezeichnung[1])

# table.one$"delta.%" <- (round(((table.one[[3]]-table.one[[2]])*100)/((table.one[[2]]+table.one[[3]])*0.5), digits = 1))
table.one$"delta.%" <- (round((100-table.one[[2]]*100/table.one[[4]]), digits = 1))
table.one$Probennummer <- validation.data$Probennummer

table.one |> 
  flextable() |>  
  theme_vanilla() |>  
  bg(bg = "grey", part = "header") |> 
  align(align = "center", part = "all") |> 
  bg(j = 6, bg = scales::col_numeric(palette = c("blue", "green", "red"), domain = c(-40, 40))) |> 
  set_table_properties(width = 0.6, layout = "autofit")
```

\newpage

## Präzisionsdaten

```{r intra_and_inter_assay_coefficient_of_variability, echo = FALSE, message = FALSE, warning=FALSE}
library(tidyverse)
library(flextable)

nameQuery <- sprintf("SELECT TestName FROM TranslationData WHERE Methode = '%s'", method)
name <- dbGetQuery(con, nameQuery)[1, 1]

# enable and register the REGEXP function in the SQLite connection
initExtension(con, extension = "regexp")

# SQL query for intra- and inter-assay precision data
query.L <- sprintf("SELECT TestName, TestStartDT, SampleID, CAST(DoseResult_c AS FLOAT) AS DoseResult, DoseUnit, Einheit_800
                  FROM DxIvalData
                  WHERE TestName = '%s' 
                    AND SampleID REGEXP '[a-zA-Z]+1' --_\\d'
                    AND DoseUnit IS NOT NULL
                  GROUP BY
                    TestStartDT;", name)

query.H <- sprintf("SELECT TestName, TestStartDT, SampleID, CAST(DoseResult_c AS FLOAT) AS DoseResult, DoseUnit, Einheit_800
                  FROM DxIvalData
                  WHERE TestName = '%s' 
                    AND SampleID REGEXP '[a-zA-Z]+2' --_\\d'
                    AND DoseUnit IS NOT NULL;", name)

# execute both queries
prc.L.data <- dbGetQuery(con, query.L) 
prc.H.data <- dbGetQuery(con, query.H)

# define data processing function
prc.data.fun <- function(prc.L.data, prc.H.data){

  #transform prc.L.data
  prc.L.data <-  prc.L.data |>  group_by(Date = as.Date(TestStartDT, format = "%m-%d-%Y")) |> slice_head(n = 5) |> ungroup()
  

  #transform prc.H.data
  prc.H.data <-  prc.H.data |>  group_by(Date = as.Date(TestStartDT, format = "%m-%d-%Y")) |> slice_head(n = 5) |> ungroup()
  
  # check the row numbers
  if(nrow(prc.L.data) >= 25 | nrow(prc.H.data) >= 25){
    # select the first 25 rows = precision data
    prc.L.data <- head(prc.L.data, 25)
    prc.H.data <- head(prc.H.data, 25)
    
    # proceed with table creation
    prc.table.fun(prc.L.data, prc.H.data)
  } else {
    # return an error message
    message("Not enough data available for precision analysis")
    return(NULL)
  }
}

prc.table.fun <- function(prc.L.data, prc.H.data){
 
    # building the CLSIEP15 table
    L.long <- data.frame(
      rep = rep(1:5, each = 5),
      name = paste(prc.L.data$SampleID[1:25], rep(1:5, each = 5), sep = "_"),
      value = prc.L.data$DoseResult[1:25]
    )
    
    H.long <- data.frame(
      rep = rep(1:5, each = 5),
      name = paste(prc.H.data$SampleID[1:25], rep(1:5, each = 5), sep = "_"),
      value = prc.H.data$DoseResult[1:25]
    )
    
    library(CLSIEP15)
    prc.data.L <- calculate_aov_infos(L.long)
    prc.data.H <- calculate_aov_infos(H.long)
    
    
    
    val.prec <- read_excel("vdata _DxI.xlsx", sheet = "PREC")
    
    intra.df <- data.frame(
      "Intra Assay" = c("n", "Zielwert", "Mittelwert", "SD", "VK (%)"),
      L = c(
        paste(prc.data.L$N),
        paste(val.prec$Ziel_intra1[1]),
        paste(round(prc.data.L$mean, 2) ),
        paste(round(prc.data.L$sd, 2) ),
        paste(round(prc.data.L$CVR, 2) )
      ),
      H = c(
        paste(prc.data.H$N),
        paste(val.prec$Ziel_intra2[1]),
        paste(round(prc.data.H$mean, 2) ),
        paste(round(prc.data.H$sd, 2) ),
        paste(round(prc.data.H$CVR, 2) )
      )
    )
    
    inter.df <- data.frame(
      "Inter Assay" = c("n", "Zielwert", "Mittelwert", "SD", "VK (%)"),
      L = c(
        paste(prc.data.L$n),
        paste(val.prec$Ziel_inter1[1]),
        paste(round(prc.data.L$mean, 2) ),
        paste(round(prc.data.L$sd, 2) ),
        paste(round(prc.data.L$CVWL, 2) )
      ),
      H = c(
        paste(prc.data.H$n),
        paste(val.prec$Ziel_inter2[1]),
        paste(round(prc.data.H$mean, 2) ),
        paste(round(prc.data.H$sd, 2) ),
        paste(round(prc.data.H$CVWL, 2) )
      )
    )
    
    intra.df.ft <- flextable(intra.df)
    intra.df.ft <- align(intra.df.ft, align = "right", part = "all")
    intra.df.ft <- autofit(intra.df.ft)
    intra.df.ft <- add_footer_lines(intra.df.ft, "")
    intra.df.ft <- bg(intra.df.ft, bg = "grey", part = "header")
    
    inter.df.ft <- flextable(inter.df)
    inter.df.ft <- align(inter.df.ft, align = "right", part = "all")
    inter.df.ft <- autofit(inter.df.ft)    
    inter.df.ft <- add_footer_lines(inter.df.ft, "")
    inter.df.ft <- bg(inter.df.ft, bg = "grey", part = "header")
    
    # Return the tables so they can be rendered in the document
    list(intra = intra.df.ft, inter = inter.df.ft)
}

ft <- prc.data.fun(prc.L.data, prc.H.data)
if(!is.null(ft$intra)){
  ft$intra
  }else{
  cat("Nicht genug Daten verfügbar für die Intra-Assay-Präzisionsanalyse")
}

if(!is.null(ft$inter)){
  ft$inter
  }else{
  cat("Nicht genug Daten verfügbar für die Inter-Assay-Präzisionsanalyse")
  }

```




```{r intra_assay_table, echo = FALSE, message = FALSE, warning = FALSE}
# intra.df.ft <- flextable(intra.df)
# intra.df.ft <- align(intra.df.ft, align = "right", part = "all")
# intra.df.ft <- autofit(intra.df.ft)
# intra.df.ft <- add_footer_lines(intra.df.ft, "")
# intra.df.ft |> bg(bg = "grey", part = "header")

```
  

```{r inter_assay_table, echo = FALSE, message = FALSE, warning = FALSE}
# inter.df.ft <- flextable(inter.df)
# inter.df.ft <- align(inter.df.ft, align = "right", part = "all")
# inter.df.ft <- autofit(inter.df.ft)
# inter.df.ft |> bg(bg = "grey", part = "header")

```


## Korrelation

<!-- Pearsson correlation and plot, sample number n from PB.reg@data -->

```{r correlation, echo=FALSE, out.height = "80%", out.width = "80%"}

## Correlation plot with Pearsson correlation
## Creating the plot
plot(method.x, method.y, pch = 19, col = "#68228B", 
     xlab=colnames(validation.data)[1], ylab=colnames(validation.data)[2])

## Regression line
abline(lm(method.y ~ method.x), col = "red", lwd = 3)

## Pearson correlation
# text(paste("Pearson's r:", round(cor(method.x, method.y), 2)), x=max(method.x)*0.85, y=max(method.y)*0.5)
#text(paste("n=", nrow(PB.reg@data)), x=max(method.x)*0.85, y=max(method.y)*0.4)
text.block <-  paste("Pearson's r:", round(cor(method.x, method.y), 2), "\nn=", nrow(PB.reg@data)) 
mtext(text.block, side = 1, line = 3, cex = 1, col = "red", adj = 0)

# paste("n=", nrow(PB.reg@data))



```


\newpage
## Passing Bablok

<!-- Passing Bablok Plot mit Steigung, Achsenabschnitt, Spearman's correlation  -->

```{r PB, echo=FALSE, out.height = "80%", out.width = "80%"}

MCResult.plot(PB.reg, equal.axis = TRUE, x.lab = colnames(validation.data)[1], y.lab = colnames(validation.data)[2], points.col = "#68228B", points.pch = 19, ci.area = TRUE, ci.area.col = "#0000FF50", main = paste("Validation", colnames(validation.data)[2], "vs", colnames(validation.data)[1]), sub = "", add.cor = TRUE, cor.method = "spearman", add.grid = FALSE, points.cex = 1)
##Angabe Steigung und Achsenabschnitt und CI
intercept_est <- PB.reg@para[1]
intercept_lci <- PB.reg@para[5]
intercept_uci <- PB.reg@para[7]
gradient_est <- PB.reg@para[2]
gradient_lci <- PB.reg@para[6]
gradient_uci <- PB.reg@para[8]
alpha_ci <- PB.reg@alpha[1]
text(cex=.65,x=max(validation.data[,1:2])*0.8,y=max(validation.data[,1:2])*0.49,sprintf("Gradient : %4.2f (%4.2f - %4.2f)", gradient_est, gradient_lci, gradient_uci))
text(cex=.65,x=max(validation.data[,1:2])*0.8,y=max(validation.data[,1:2])*0.42,sprintf("Intercept : %4.2f (%4.2f - %4.2f)", intercept_est, intercept_lci, intercept_uci))
text(cex=.65,x=max(validation.data[,1:2])*0.8,y=max(validation.data[,1:2])*0.35, sprintf("alpha : %4.2f", alpha_ci))

```

```{r coef_plot, echo = FALSE, warning = FALSE, message = FALSE}
fitPaBa <- mcreg(as.matrix(validation.data[,1:2]), method.reg="PaBa", na.rm=TRUE)
fitlr <- mcreg(as.matrix(validation.data[,1:2]), method.reg="LinReg", na.rm=TRUE)
compareFit(fitlr, fitPaBa)
```

\newpage

## Bland-Altman

```{r BA, echo=FALSE, out.height = "80%", out.width = "80%"}
MCResult.plotDifference(PB.reg)
```

```{r BArel, echo=FALSE, out.height = "80%", out.width = "80%"}

MCResult.plotDifference(PB.reg, plot.type = 8, main = "rel Difference plot")
```

```{r Bias, echo=FALSE, out.height = "90%", out.width = "90%"}
## Calculation of models
m2 <- mcreg(method.x,method.y,method.reg="PaBa", method.ci="bootstrap",
            method.bootstrap.ci="BCa",mref.name=colnames(validation.data)[1],
            mtest.name=colnames(validation.data)[2], na.rm=TRUE)
## Drawing of proportional bias
plotBias(m2, ci.area=TRUE, ci.border=TRUE, cex.sub=0.2)

```

```{r Bias_prop, echo=FALSE, out.height = "90%", out.width = "90%"}
plotBias(m2, ci.area=TRUE, ci.border=TRUE, prop=TRUE, cex.sub=0.2)
```

\newpage

# Schlussfolgerung und Freigabe



<!-- User Input zur Beurteilung und Freigabe -->



```{r Schlussfolgerung, echo = FALSE}
block_pour_docx("blocks_Akzeptanzkriterien.docx")
```
---

**Zentrum für Labormedizin St. Gallen, `r paste(format(Sys.time(), '%A %d. %B %Y'))`**

\newpage

--- 

#### Data is processed using R language^1^, mcr package^2^ and flextable package^3^. Rmarkdown^4^, Officedown^5^ and Officer^6^ are used for converting results into Word, PDF and HTML files. This project was inspired by Daniel Holmes (UBC, CA)^7^, Burak Bahar (Washington, USA)^8^ and David Gohel (Roubaix, F)^9^.
  
#### References and packages:
  
1.  R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. Version: `r getRversion()` URL: <https://www.R-project.org>
2.  mcr: Method Comparison Regression. Version: `r packageDescription("mcr")$Version` URL: <http://CRAN.R-project.org/package=mcr>
3.  flextable: a framework for easily creating tables. Version: `r packageDescription("flextable")$Version` URL: <http://CRAN.R-project.org/package=flextable>
4.  rmarkdown: Dynamic Documents for R. Version: `r packageDescription("rmarkdown")$Version` URL: <http://rmarkdown.rstudio.com>
5.  officedown: Formatting Microsoft documents produced by RMarkdown. R Version: `r packageDescription("officedown")$Version` URL: <http://CRAN.R-project.org/package=officedown>
6.  officer: Manipulation of Microsoft Word and PowerPoint Documents. R Version: `r packageDescription("officer")$Version` URL: <http://CRAN.R-project.org/package=officer>
7.  The Lab-R-torian: URL: <https://labrtorian.com/>
8.  An interactive website for analytical method comparison and bias estimation: URL: <https://bahar.shinyapps.io/method_compare/>
9.  SOLUTIONS ET FORMATIONS EN DATA-SCIENCE: URL: <https://www.ardata.fr/>

---