---
output:
  word_document: default
  pdf_document: default
  html_document: default
  '': default
  allways_allow_html: true
---

---
output:
  html_document:
    css: "style.css"
    fig_width: 10
    fig_height: 10
    fig_caption: true
    df_print: paged
  pdf_document: default
  '': default
date: "`r format(Sys.time(), '%A %d. %B %Y')`"
---

```{r setup, include=FALSE}
library(knitr)
library(parallel)
library(robslopes)
library(readxl)
library(mcr)
opts_chunk$set(echo = TRUE)
```

<!-- Prepare libraries and import data from Excel -->

<!-- create vectors method.x and method.y, run Passing Bablok regression -->

<!-- change column names in PB.reg@mnames to prepare for dynamic title-, axis- & legend labels-->

```{r prepareData, echo=FALSE}

## Import Data from a xlsx file, create the vectors for reference x and test y

val.crit <- read_excel("C:\\R_local\\vdata.xlsx", sheet = "CRIT")
val.info <- read_excel("C:\\R_local\\vdata.xlsx", sheet = "INFO")
val.data <- read_excel("C:\\R_local\\vdata.xlsx", sheet = "DATA")

method.x <- val.data[[1]]
method.y <- val.data[[2]]
## PaBa (formal class names: PB.reg) regression, rename column titles in PB.reg@mnames
PB.reg <- mcreg(method.x,method.y, method.reg = "PaBa")
PB.reg@mnames[1] <- colnames(val.data)[1]
PB.reg@mnames[2] <- colnames(val.data)[2]

```

# Validierungsbericht  
 

## `r paste(val.info$Messgröss[1])`  
------------------------------------
  
|**EINLEITUNG**| 



Validierungsanalge zu QM-Dokumenten|              |
---------------------------------- | ------------ | ----------------
Projekt                            |`r paste(val.info$Projekt[1])`|`r paste(val.info$Projekt_Titel[1])`
Mutation                           |`r paste(val.info$Mutation[1])`|`r paste(val.info$Mutations_Titel[1])`  
  
Validierungsanalge zu QM-Dokumenten|           |
---------------------------------| ------------ | ----------------
Projekt                          |`r paste(val.info$Projekt[1])`|`r paste(val.info$Projekt_Titel[1])`
Mutation                         |`r paste(val.info$Mutation[1])`|`r paste(val.info$Mutations_Titel[1])`  

